The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-05-20 ms.tex
Merged.

In this section, we describe our cosmological radiation hydrodynamics
simulation suite with sub-pc resolution, focusing on first the
formation and feedback of Pop III stars, the transition to Pop II star
formation, and finally the formation of the first galaxies.  We then
detail our star formation and feedback algorithms.  We run a total of
eight different simulations, varying physical parameters.  In the
following description, we quote the parameters used in our fidicual
model and describe their variations later in Sec. \ref{sec:config}.

@@

We initialize the simulation with \textsc{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
variables having their usual definitions.  We use a maximum refinement
level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
We stop the simulation at $z=7$ to avoid any large-scale modes with $r
\sim L_{\rm box}/2$ entering the non-linear growth regime.  At the
final redshift, this simulation has $1.4 \times 10^8$ computational
cells and required 250,000 CPU hours, using 512 cores.

@@

We perform nine different simulations with the same initial conditions.
The baseline model considers (a) primordial cooling with 9 species of
hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

>>>>

In this section, we describe our cosmological radiation hydrodynamics
simulation suite with sub-pc resolution, focusing on first the
formation and feedback of Pop III stars, the transition to Pop II star
formation, and finally the formation of the first galaxies.  We then
detail our star formation and feedback algorithms.  We run a total of
ten different simulations, varying physical parameters.  In the
following description, we quote the parameters used in our reference
model and describe their variations later in Sec. \ref{sec:config}.

@@

We initialize the simulation with \textsc{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP $\Lambda$CDM+SZ+LENS best fit
\citep{WMAP7}: $\Omega_M = 0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b
= 0.0449$, $h = 0.71$, $\sigma_8 = 0.81$, and $n = 0.963$ with the
variables having their usual definitions.  We use a maximum refinement
level of $l = 12$, resulting in a maximal comoving resolution of 1 pc.
We stop the simulation at $z=7$ or when the volume reaches an ionized
fraction of 0.9.  The first stopping point prevents any large-scale
modes with $r \sim L_{\rm box}/2$ from entering the non-linear growth
regime.  At the final redshift, the baseline simulation has $1.4
\times 10^8$ computational cells and required 250,000 CPU hours, using
512 cores.

@@

We perform ten different simulations with the same initial conditions.
The reference model considers (a) primordial cooling with 9 species of
hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:
